### 2022-07-05 paper/main.tex
more citations

\par Crime has long shaped people's lives. The fear of crime has inspired historical events (REF), shaped elections (REF), and motivated social movements (REF). While fear of crime has occurred organically throughout history, some people or groups have elevated crime cases for political or monetary gain (REF). The media is one such group that potentially seeks to gain from crime discussion. The relationship between the media and perceptions of crime has been the subject of many studies in fields such as sociology and criminology (REF). Through mediums such as television (REF) and print (REF), researchers have long analyzed how the prevalence of crime reporting might affect consumer's perceptions of public safety.

\par While traditional media such as television and newspapers are frequently the subject of research, they have become increasingly less relevant. As traditional media declines, social media, such as Twitter, Facebook, and Reddit, has risen in its place. As a result, an increasing number of people consume news through social media (REF), which includes topics such as crime. However, social media is not without its flaws. Due to the free and open nature of who can post on social media, submissions containing misinformation (REF) and manipulation of content (REF) have remained a challenge for social media companies to reign in.

\par As social media begins to fill traditional media's niche, one might wonder how the landscape of crime reporting and discussion might change. In this work, we analyze the discussion of crime on the social media website Reddit. Specifically, we examine how crime discussion takes shape on the 384 communities, known as subreddits, that represent the Metropolitan Statistical Areas of the United States. To measure crime discussion, we have developed a Reddit scraper to fetch all of the posts from the 384 communities. We have also developed techniques to identify posts that discuss crime while minimizing false positives. We analyze the data collected by the scraper to determine a community's level of crime discussion in comparison to its population, voting patterns, and documented crime rate. Lastly, we dive into the posting histories of users who post to Reddit's New York City community to identify any further trends or patterns.

@@

\par Before we begin the gathering of the data, we must first understand the scale at which the data should be collected. First, we are collecting data that pertains to the United States. Second, in a general sense, we want to measure at a city-level scale. The city is the base-level at which a critical mass of population can support an online community; a city provides a geographic center and a name to associate with a community. However, the definition of a city is rather murky. The definition varies on a state-by-state basis due to the nature in which a state delineates county-level subdivisions. All states are broken down into counties, but differ in how counties are partitioned. For example, New York breaks down counties into towns, cities, and villages, while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated. In this way, we can think of city limits and city populations as somewhat arbitrary. There is no consistent, uniform definition, so cities should not be compared to each other. To equalize these differences, we use statistical area definitions provided by the United States Census Bureau.

@@

\par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on. Their shapes are generally compact and do not have any sort of uniform governing body. To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale. MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county \cite{censusmetro}. In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities. MSAs also lump together nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis. As of March 2020, there are 384 Metropolitan Statistical Areas \cite{censusmetro}, each with a corresponding Reddit community.

@@

\par When analyzing our selected Reddit communities, we need to consider the geospatial aspects of social media. There is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community. Scellato et al. measure the nature of geographic social networks \cite{sscellato}. They compared the geospatial proximity of graph-connected users on four social media sites. They found that sites, such as FourSquare, that had an explicitly geographic nature had a higher degree of locality. However, sites that focused more on general information exchanges showed less geographic clustering. The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it. There is not a geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering.

@@

% REFS:

% https://policycommons.net/artifacts/1817184/news-consumption-across-social-media-in-2021/2554124/
% https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2771080

\par Traditional media, such as television, newspapers, magazines, and radio, have long been intertwined with a fascination for crime. Live manhunts for suspects such as OJ Simpson \cite{yjewkes} and the Boston Bombers (REF ?) have captured and enthralled viewers and readers. However, while high-profile cases garner much of the attention, local and lower-profile cases often inhabit newspaper columns and television segments. It is with these cases that people grow uneasy with the sense of public safety in their community. A flurry of reporting on violent acts can increase worry, stress, and fear that crime is rising, even if the documented crime statistics show that crime has not increased \cite{lheath}.

\par An increase in a fear of crime can have implications beyond elevated negative emotions. Fear of crime has far-reaching political, social \cite{yjewkes}, and institutional \cite{vsacco} impacts. Belief in excessive amounts of crime can lead to loss of community cohesion \cite{lheath}. Heath and Gilbert found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased \cite{lheath}. Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles. Those that perceived crime to be worse than others were more likely to perform excessive crime prevention actions, such as not leaving their house or engaging with the neighborhood.

@@

\par While the relationship between traditional media and crime has been thoroughly researched, the relationship between social media and crime has not been as rigorously explored. Social media, which originally started as a method of connecting with friends and family, has grown and evolved beyond its humble beginnings. Social media sites, such as Twitter, are now significant sources of new for many Americans (REF - LR: What is twitter?). (REF 9) found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit. This trend coincides with the decline of traditional media. Printed media, such as newspapers and magazines, as well as televised media, has consistently declined since the explosive growth of the Internet (REF 10). Despite this, research on social media remains sparse.

% Paragraph about relevant paper

(REF) detail the ecosystem of crime discussion on Twitter. Specifically, they look at how often crime discussion appears in Tweets posted from users in Latin American countries. Using Twitter's geolocation tags, Tweets are subdivided down to the municipality that the original user posted from. From here, the authors compared Twitter crime discussion rates to city-level documented crime rates. They did not find a correlation between high frequencies of crime-related Tweets and high rates of reported crime. The authors conclude that the Tweets do not accurately represent actual rates of crime, but they effectively capture the worry of crime in a community.

@@

(REF) introduce an interesting observation: some of the crime-related Tweets are highly sensationalized or completely untrue. In this way, social media differs from traditional media. Traditional media acts as a gatekeeper (REF 2), where only select stories and viewpoints emerge and some degree of factchecking generally exists (REF ?). Social media, on the other hand, allows for a more diverse set of viewpoints and opinions. However, as there is generally a limited amount of moderation (REF ?) on social media platforms, blatantly false stories can spread across sites (REF). This proliferation of misinformation has become increasingly impactful in the United States. It has affected important events in recent American history, including presidential elections (REF ?) and the the response to the Covid-19 pandemic (REF ?). Despite attempts to curb the spread of misinformation on social media (REF ?), falsehoods and panics continue to spread across the web.

>>>>

\par Crime has long shaped people's lives. The fear of crime has inspired historical movements \cite{pmieszkowski} and shaped elections \cite{jliu}. While fear of crime has occurred organically throughout history, some have sought to gain politically or monetarily from a saturation of worry. One method in which this happens is through the use of media \cite{vsacco}. Through mediums such as television \cite{jshanahan} and print \cite{lheath}, researchers have long analyzed how the prevalence of crime reporting might affect consumer's perceptions of public safety.

\par While traditional media, such as television and newspapers, are frequently the subject of crime-relationship research, they have grown increasingly irrelevant. As traditional media declines \cite{rnielsen}, social media, such as Twitter, Facebook, and Reddit, has risen in its place. Due to this shift in media consumption patterns, an increasing number of people receive news through social media \cite{hkwak}, including stories that focus on crime. However, social media faces some flaws not found in the traditional media landscape. Due to the free and open nature of who can post on social media, submissions containing misinformation \cite{kognyanova} and manipulation of content \cite{aarif} have remained a challenge for social media companies to reign in.

\par As social media begins to fill traditional media's niche, one might wonder how the landscape of crime reporting and discussion might change. In this work, we analyze the discussion of crime on the social media website Reddit. Specifically, we examine how crime discussion takes shape on the 384 communities, known as subreddits, that represent the Metropolitan Statistical Areas of the United States. To measure crime discussion, we have developed a Reddit scraper to fetch submitted posts from the 384 selected subreddits. We then perform textual analysis techniques to identify posts that discuss crime while minimizing false positives. We analyze the data collected by the scraper to determine a community's level of crime discussion in comparison to its population, voting patterns, and documented crime rate. Lastly, we dive into the posting histories of users who post to Reddit's New York City community to identify any further trends or patterns.

@@

\par Before we begin the gathering of the data, we must first understand the scale at which the data should be collected. First, we are collecting data that pertains to the United States. Much research has focused on the relationship between crime and media specifically within the United States. The United States Census Bureau also provides plentiful contextual and reference data. Second, in a general sense, we want to measure at a city-level scale. The city is the base-level at which a critical mass of population can support an online community; a city provides a geographic center and a name to associate with a community. However, the definition of a city is rather murky. The definition varies on a state-by-state basis due to the nature in which a state delineates county-level subdivisions. All states are broken down into counties, but differ in how counties are partitioned. For example, New York breaks down counties into towns and cities, while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated. In this way, we can think of city limits and city populations as somewhat arbitrary. There is no consistent, uniform definition, so cities should not be compared to each other. To best equalize these differences, we use statistical area definitions provided by the United States Census Bureau.

@@

\par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on. Their shapes are generally compact and do not have any sort of uniform governing body. To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale. MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county \cite{censusmetro}. In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities. As of March 2020, there are 384 Metropolitan Statistical Areas \cite{censusmetro}, each with a corresponding Reddit community.

@@

\par When analyzing our selected Reddit communities, we need to consider the geospatial aspects of social media. In some sites, specific geographic location is intrinsic to the functionality of the product, whereas in others, anyone can browse a community for somewhere far away. For example, on Reddit there is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community. Scellato et al. measure the geographic nature of social networks through the comparison of geospatial proximity of graph-connected users on four social media sites \cite{sscellato}. They found that sites, such as FourSquare, that had an explicitly geographic nature produced a higher degree of locality. However, sites that focused more on general information exchanges, such as Twitter, showed less geographic clustering.

\par The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it. There is no geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering. In this way, we must determine if those posting in a certain community are truly local.

@@

\par Traditional media, such as television, newspapers, magazines, and radio, has long been intertwined with a fascination for crime. Live manhunts for suspects such as OJ Simpson \cite{yjewkes} and the Boston Bombers \cite{aspeckhard} have captured and enthralled viewers and readers. However, while high-profile cases garner much of the attention, local and lower-profile cases often inhabit newspaper columns and television segments. It is with these cases that people grow uneasy with the sense of public safety in their community. A flurry of reporting on violent acts can increase worry, stress, and fear that crime is rising, even if the documented crime statistics show that crime has not increased \cite{lheath}.

\par An increase in a fear of crime can have implications beyond elevated negative emotions. Fear of crime has far-reaching social\cite{lheath}, political \cite{yjewkes}, and institutional \cite{vsacco} impacts. Belief in excessive amounts of crime can lead to loss of community cohesion; Heath and Gilbert found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased \cite{lheath}. Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles. Those that perceived crime to be worse than others were more likely to perform excessive crime prevention actions, such as not leaving their house or engaging with the neighborhood.

@@

\par While the relationship between traditional media and crime has been thoroughly researched, the relationship between social media and crime has not been as rigorously explored. Social media, which originally started as a method of connecting with friends and family, has grown and evolved beyond its humble beginnings. Social media sites, such as Twitter, are now significant sources of new for many Americans \cite{hkwak}. Walker and Masta found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit \cite{pewresearch}. This trend coincides with the decline of traditional media. Printed media, such as newspapers and magazines, as well as televised media, have consistently declined since the explosive growth of the Internet \cite{rnielsen}. Despite this, research on social media remains sparse.

Curiel et al. detail the ecosystem of crime discussion on Twitter \cite{curiel}. Specifically, they look at how often crime discussion appears in Tweets posted from users in Latin American countries. Using Twitter's geolocation tags, Tweets are subdivided down to the municipality that the original user posted from. From here, the authors compared Twitter crime discussion rates to city-level documented crime rates. They did not find a correlation between high frequencies of crime-related Tweets and high rates of reported crime. The authors conclude that the Tweets do not accurately represent actual rates of crime, but they effectively capture the worry of crime in a community.

@@

Curiel et al. introduce an interesting observation: some of the crime-related Tweets are highly sensationalized or completely untrue \cite{curiel}. In this way, social media differs from traditional media. Traditional media acts as a gatekeeper, where only select stories and viewpoints emerge and factchecking generally exists in mainstream publications \cite{vsacco}. Social media, on the other hand, allows for a more diverse set of viewpoints and opinions. However, as moderation policies vary \cite{szannettou} on social media platforms, blatantly false stories can spread across sites if left unchecked. This proliferation of misinformation has become increasingly impactful in the United States. It has affected important events in recent American history, including presidential elections \cite{jliu} and the the response to the Covid-19 pandemic \cite{amian} \cite{ftahmsabi}. Without intervention, falsehoods and panics continue to spread across the web.
